Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Update a comment
BCP: break code into two pieces (we still need some "separator" text)

    At this stage we do not care about invalid input or performance.
    We are happy with an implementation that works for small
    non-negative numbers.
\end{quote}

@@

instance Arbitrary Small where
  arbitrary = Small . (`mod` 10) <$> arbitrary

main = hspec spec

>>>>

    At this stage we do not think about invalid input or performance.
    We are happy with an implementation that works for small
    non-negative integers.
\end{quote}

@@

instance Arbitrary Small where
  arbitrary = Small . (`mod` 10) <$> arbitrary
\end{verbatim}
\end{quote}

\noindent TBD: can we put some useful text here, so that the code
example is divided into two pieces, and hence each piece is smaller?

\begin{quote}
\small
\begin{verbatim}
main = hspec spec
